Revealing the movement dynamics of hippocampal replay using state space modeling

### 2020-09-24 Article.tex
Update on Overleaf.

\title{Revealing the rich and varied dynamics of hippocampal replay}
\shorttitle{Replay Dynamics}

@@

Hippocampal replay events are a prototypical example of a generative representation. As animals move through space, neurons in the hippocampus preferentially fire at specific locations in an environment, and thus sets of cells fire in sequence as the animal moves through a series of locations. When the animal is asleep or immobile, hippocampal cells can be reactivated during a "sharp-wave ripple" (SWR) event. A subset of SWRs contain sequential firing similar to that seen during a previous experience or likely to occur during potential future experiences, and previous work has reported that these sequential firing events proceed at an average speed of ~10 meters / second, about 20x faster than the animal's usual movement speed \cite{NadasdyReplayTimeCompression1999, LeeMemorySequentialExperience2002, DavidsonHippocampalReplayExtended2009, KarlssonAwakereplayremote2009}.

@@

While the standard decoder approach identifies constant speed events, it does not consider events that are rejected by the statistical test, and the use of a fixed size temporal bin acts as a boxcar smoother that limits the potential movement speeds of the representation. The linear fit is also problematic, because it has the potential to reject real events that do not move at constant speeds. Approaches that focus on the order of cell activity within each event \cite{LeeMemorySequentialExperience2002, GuptaHippocampalReplayNot2010} allow for a relaxation of that linear assumption, but replace it with a loss of statistical power due to either ignoring all but the first spike from each cell or using some arbitrarily smoothed version of the spike train. These approaches also do not provide information about the dynamics of the underlying spatial representation. Moreover, there is now evidence that a subset of these events have stationary representations of a single location \cite{JaiDistincthippocampalcorticalmemory2017, FarooqEmergencepreconfiguredplastic2019}, which both approaches often exclude. In addition, these methods identify only a subset of events as containing content (typically somewhere between 10 and 45\% of the chosen events), and thereby provide little insight into the remaining majority of the events.

@@

\section*{Results}
\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure1/Figure1_v4}
\caption{Verifying the model can capture different sequence dynamics on simulated data and showing how it can classify different trajectory speeds. \textbf{(A)} We construct a firing sequence of 19 simulated place cells that exhibits three different movement dynamics. For the first 60 ms, one cell fires repeatedly, representing one stationary location. For the second 60 ms, the cells fire in sequence, representing a rapid continuous trajectory along the virtual track. For the last 60 ms, cells fire randomly, out of their spatial order, representing an incoherent spatial sequence. \textbf{(B)} Like the standard decoder, the state space model uses estimates of cells' place fields from when the animal is moving and combines them with the observed spikes in (A) to compute the likelihood of position for each time step. \textbf{(C)} The prediction from the neural data is then combined with an explicit model of each movement dynamic, which determines how latent position can change based on the posterior from the previous time step. In the stationary movement dynamic, the transition matrix is modeled as the identity matrix because the position remains the same. In the continuous movement dynamic, the transition matrix is modeled as a Gaussian random walk, meaning the next possible position is likely to be spatially close to the previous position. In the fragmented movement dynamic, the transition matrix is modeled as uniform, meaning the next position is equally likely to be any possible position. Note that the movement dynamics displayed only reflect the within-state movement dynamics. \textbf{(D)} The probability of remaining in a particular dynamic versus switching to another dynamic is modeled as having a high probability of remaining in a particular dynamic with a small probability of switching to one of the other dynamics at each time step. \textbf{(E)} The state space model uses the components in A-D over all time to decode the joint probability of latent position and dynamic state. The joint probability can be summarized by marginalizing over latent position (left panel) to get the probability of each dynamic state over time. The summed posterior across states also provides an estimate of latent position over time (right panel). \textbf{(F)} The probability of each dynamic depends heavily on the speed of the trajectory, as we show using a range of simulated spiking sequences each moving at a constant speed. The lines correspond to the average probability of that dynamic for a given constant velocity sequence. We use a 0.8  threshold (dotted line) to classify each sequence based on the state or states which contribute maximally to the posterior. 
}
\label{1}
\end{figure*}
\subsection*{Overview of the model}
We begin with an application of the model to simulated data, both to validate the model and to provide intuition (Figure \ref{1}). We simulated 19 Poisson spiking cells with Gaussian place fields on a 180 cm virtual linear track. Each place field has a 36 cm variance and a 15 Hz peak firing rate, which is spaced every 10 cm along the virtual track. We then construct an 180 ms spiking sequence and apply our decoding algorithm in Figure \ref{1}A. For the first 60 ms of this sequence, a single place cell fires repeatedly, resulting in the extended representation of a single location. For the second 60 ms of the sequence, the cells fire in sequential spatial order, representing a fast moving trajectory across the virtual linear track. For the last 60 ms of the sequence, the cells fire in an incoherent spatial order. These three firing patterns represent three different types of sequence dynamics that could be expressed during replay events, which we call stationary, continuous, and fragmented, respectively. The goal of our model is to characterize SWRs in terms of a mixture of these three dynamics at every time point.

Decoding the spiking sequence dynamics requires specifying two elements: the data model---how the spikes relate to position---and the movement dynamics model---how the position can change over time. For the data model, our decoder is the same as the standard ("Bayesian") decoder \cite{DavidsonHippocampalReplayExtended2009, PfeifferAutoassociativedynamicsgeneration2015, StellaHippocampalReactivationRandom2019}. We compute an estimate of how each cell's firing rate varies over position during movement (i.e. the place field, Figure \ref{1}B). This is used during decoding to compute the Poisson likelihood of position over time given the spiking sequence of interest. In contrast to the standard decoder, we can use arbitrarily small time bins (in our case 2 ms vs. 20 ms or more) because we are able to take advantage of the prior placed on the dynamics by the state space model. This allows us to detect changes on smaller time scales than would be possible with the standard decoder.

Next, we specify a movement dynamics model for how latent position---the "mental" position of the animal represented by the cells---evolves over time (Figure \ref{1}C). We do this by defining a state transition matrix, which defines how the latent position can move from the previous time step. Previous findings suggest that replay may exhibit at least three distinct types of movement: stationary \cite{JaiDistincthippocampalcorticalmemory2017, FarooqEmergencepreconfiguredplastic2019}, rapid continuous \cite{DavidsonHippocampalReplayExtended2009}, and fragmented, which could correspond to both extended spatially incoherent representations and representations that jump from one position to another in a short time period \cite{PfeifferAutoassociativedynamicsgeneration2015}. We therefore define state transition models to capture each of these dynamics.

In the stationary dynamic, the latent position does not change between time steps. The state transition matrix can thus be defined as an identity matrix, which predicts the next position will be the same as the last position. In the continuous dynamic, the latent position is most likely to be  "spatially close" to the position in the previous time step, so we use a Gaussian random walk state transition matrix. This means that, for a given latent position, the probability of moving to another position is modeled by a Gaussian centered at that position and "spatially close" is defined by the variance of the Gaussian. In our case, since replay has been shown to move at speeds much faster than the animal's speed \cite{DavidsonHippocampalReplayExtended2009, PfeifferAutoassociativedynamicsgeneration2015}, we set the variance of the Gaussian to 6.0 cm. This ensures that with a 2 ms time step, the latent position is 95\% likely to be within 4.90 cm of the previous latent position (or equivalently, this means that latent speeds from 0 to ~25 m/s are most likely).  Finally, in the fragmented dynamic, the latent position can move to any available position instantaneously. We model this using a uniform state transition matrix, which makes transitions to all positions equally likely.

Finally, we specify how likely each dynamic is to persist in time versus changing to another dynamic (Figure \ref{1}D). In order to be conservative, we assume that each dynamic is likely to dominate for \texttildelow100 ms, which is approximately the duration of a SWR event. There is, however, a small probability of switching to one of the other dynamics. Accordingly, we set the probability of staying in a dynamic to 0.98 for each 2 ms time step. Because the probability of changing dynamics follows a geometric distribution, this corresponds to an expected duration of 100 ms for staying in a particular dynamic. Importantly, the data drives the estimated dynamic, so even if the probability of a particular dynamic is high, data providing clear evidence for a change in dynamic can, within the time frame of \texttildelow10 ms, drive a change to a different estimated dynamic. In line with this, note that below we show that our results are relatively insensitive to the value of this parameter.

Once we have specified the data and dynamics model, we have fully specified the state space model. We use acausal decoding, meaning that we use all information from the past and future spikes, to estimate the joint posterior probability of position and dynamic (see Methods). With this, we can summarize the resulting posterior with two quantities: the mixture probability of each dynamic over time (by marginalizing over position) and the probability of latent position over time, irrespective of dynamic (by marginalizing over dynamic; Figure \ref{1}F, left and right plot respectively).

An examination of the two summaries shown in Figure \ref{1}F reveals that that the model successfully captures the dynamics of the population spiking activity in Figure \ref{1}A. The stable firing of the one active neuron indicates a stationary representation, and accordingly, the probability of the stationary dynamic is high at the beginning of the simulated replay. A change in the data then drives a rapid transition to the continuous dynamic, reflecting the trajectory-like spatially sequential spiking from the population of cells. Subsequently, as the population activity becomes spatially incoherent, the fragmented dynamic dominates for the last third of the simulated event. Importantly, these dynamics also inform the estimate of latent position of the animal, and the correct assignment of dynamic reduces the variance of the latent position estimate.

The specification of these dynamics allows the model to capture a wide range of movement speeds for the latent position. To demonstrate this, we applied the model to simulated trajectories of increasing speed (Figure \ref{1}G), from 1 cm/s to 10,000 m/s. From this, we can see that not only are there regions of speed that correspond to our three dynamics being highly probable (where we define highly probable to be over 0.8 probability), there are intermediate speeds where two of the dynamics exhibit relatively high probability; and where the sum of two of the dynamics' probabilities exceeds 0.8. In this manuscript, we will refer to these as mixture dynamics. For example, when the stationary state has a probability of 0.6 and the continuous has a probability of 0.4, we call this a stationary-continuous mixture (light blue, Figure \ref{1}G). By using this classification scheme, we can characterize the speed or set of speeds in a replay by its dynamics.

@@

One of our criteria for a more optimal method is for it to use all of the available spiking data. Using only clustered spikes discards any spike events that cannot be uniquely assigned to a putative single neuron, substantially reducing the amount of information that the resultant decoding can use. Additionally, spike sorting is not necessary to recover the underlying neural population dynamics \cite{TrautmannAccurateEstimationNeural2019}, is time-consuming, and often requires inclusion decisions that can vary widely across experimenters. We therefore adopted a "clusterless" approach which directly relates spikes and their multiunit spike waveform features to position without spike sorting, which we call clusterless decoding (see Methods). Clusterless decoding previously has been used to successfully identify theta sequences and replay sequences in the hippocampus (\cite{KloostermanBayesiandecodingusing2014, ChenTransductiveneuraldecoding2012,DengRapidclassificationhippocampal2016, KayConstantSubsecondCycling2020}). Applying a clusterless decoder to the same SWR event, we get similar classification of the sequence (Figure \ref{2}B, D), both with 1D linearized position and 2D position (Figure \ref{fig:Figure2-Figure supplement 1}B). As predicted, the spatial extent of the event is longer and the estimate of the posterior probability of position is narrower for the clusterless model. This reflects the clusterless model's access to a larger pool of data that provides more information about the extent of the event and more certainty in the latent position and the dynamic (Figure \ref{2}D vs C).

@@

Using a 0.8 threshold, we were able to classify 89\% (23382 of 26160) of SWRs as containing at least one of the three states or common state mixtures. To ensure that this depended on the sequential firing of spatially tuned cells in the hippocampus, we resampled position with replacement for two recording sessions, shuffling the relationship between spiking and spatial information and then fitting the encoding model. We then decoded the same SWR events containing the same spikes. Only 9\% of the SWRs were classified in the shuffled datasets, a value that was significantly less than that seen for the real data (p=0.02 for recording session 1, p=0.02 for recording session 2, Figure \ref{fig:Figure3-Figure supplement 2}).

@@

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure1-supplemental1/Figure1_v2_supplemental1}
\caption{The model is robust to change of the probability of persisting in the same dynamic. Each plot shows the probability of each dynamic on simulated data example from Figure 1 with a different diagonal value---which governs the probability of remaining in that state. The off-diagonal values---the probability of switching to one of the other dynamics---are set to be equally likely with the remainder of the probability, as in Figure 1D. The first plot (upper left) shows the case when all dynamics are equally likely. The diagonal increases from left to right, top to bottom, until the case where the diagonal is one and the off-diagonal is zero---i.e. the case where there is no probability of switching to another state.}
\label{fig:Figure1-Figure supplement 1}
\end{figure*}

>>>>

\title{Revealing the movement dynamics of hippocampal replay using state space modeling}
\shorttitle{Replay Dynamics}

@@

Hippocampal replay events are a prototypical example of a generative representation. As animals move through space, neurons in the hippocampus preferentially fire at specific locations in an environment, and thus sets of cells fire in sequence as the animal moves through a series of locations. When the animal is asleep or immobile, hippocampal cells can be reactivated during a "sharp-wave ripple" (SWR) event. A subset of SWRs contain sequential firing similar to that seen during a previous experience or likely to occur during potential future experiences, and previous work has reported that these sequential firing events proceed at an average speed of ~10 meters per second, about 20x faster than the animal's usual movement speed \cite{NadasdyReplayTimeCompression1999, LeeMemorySequentialExperience2002, DavidsonHippocampalReplayExtended2009, KarlssonAwakereplayremote2009}.

@@

While the standard decoder approach identifies constant speed events, it does not consider events that are rejected by the statistical test, and the use of a fixed size temporal bin acts as a boxcar smoother that limits the potential movement speeds of the representation. The linear fit is also problematic, because it has the potential to reject real events that do not move at constant speeds. Approaches that focus on the order of cell activity within each event \cite{LeeMemorySequentialExperience2002, GuptaHippocampalReplayNot2010} allow for a relaxation of that linear assumption, but replace it with a loss of statistical power due to either ignoring all but the first spike from each cell or using an arbitrarily smoothed version of the spike train. These approaches also do not provide information about the dynamics of the underlying spatial representation. Moreover, there is now evidence that a subset of these events have stationary representations of a single location \cite{JaiDistincthippocampalcorticalmemory2017, FarooqEmergencepreconfiguredplastic2019}, which both approaches often exclude. In addition, these methods identify only a subset of events as containing content (typically somewhere between 10 and 45\% of the chosen events), and thereby provide little insight into the remaining majority of the events.

@@

\section*{Results}
\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure1/Figure1_v6}
\caption{Verifying the model can capture different sequence dynamics on simulated data. \textbf{(A)} We construct a firing sequence of 19 simulated place cells that exhibits three different movement dynamics. For the first 60 ms, one cell fires repeatedly, representing one stationary location. For the second 60 ms, the cells fire in sequence, representing a rapid continuous trajectory along the virtual track. For the last 60 ms, cells fire randomly, out of spatial order, representing an fragmented spatial sequence. \textbf{(B)} Like the standard decoder, the state space model uses estimates of cells' place fields from when the animal is moving and combines them with the observed spikes in (A) to compute the likelihood of position for each time step. \textbf{(C)} The prediction from the neural data is then combined with an explicit model of each movement dynamic, which determines how latent position can change based on the position in the previous time step. We show the probability of the next position bin for each movement dynamic model (shading). Zero here represents the previous position. \textbf{(D)} The probability of remaining in a particular movement dynamic versus switching to another dynamic is modeled as having a high probability of remaining in a particular dynamic with a small probability of switching to one of the other dynamics at each time step. \textbf{(E)} The state space model uses the components in A-D over all time to decode the joint probability of latent position and dynamic state. The joint probability can be summarized by marginalizing over latent position (left panel) to get the probability of each dynamic state over time. The summed posterior across states also provides an estimate of latent position over time (right panel). \textbf{(F)} The probability of each dynamic depends heavily on the speed of the trajectory, as we show using a range of simulated spiking sequences each moving at a constant speed. The lines correspond to the average probability of that dynamic for a given constant velocity sequence. We use a 0.8  threshold (dotted line) to classify each sequence based on the state or states which contribute maximally to the posterior. 
}
\label{1}
\end{figure*}
\subsection*{Overview of the model}
We begin with an application of the model to simulated data, both to validate the model and to provide intuition (Figure \ref{1}). We simulated 19 Poisson spiking cells with Gaussian place fields on a 180 cm virtual linear track. Each place field has a 36 cm variance and a 15 Hz peak firing rate, which is spaced every 10 cm along the virtual track. We then construct an 180 ms spiking sequence and apply our decoding algorithm in Figure \ref{1}A. For the first 60 ms of this sequence, a single place cell fires repeatedly, resulting in the extended representation of a single location. For the second 60 ms of the sequence, the cells fire in sequential spatial order, representing a fast moving trajectory across the virtual linear track. For the last 60 ms of the sequence, the cells fire in an incoherent spatial order. These three firing patterns represent three different types of sequence dynamics that could be expressed during replay events, which we call stationary, continuous, and fragmented, respectively. The goal of our model is to characterize SWRs in terms of a mixture of these three dynamics at every time point.

Decoding the spiking sequence dynamics requires specifying two elements: the data model---how the spikes relate to position---and the movement dynamic models---how the position can change over time given a movement dynamic. For the data model, our decoder is the same as the standard ("Bayesian") decoder \cite{DavidsonHippocampalReplayExtended2009, PfeifferAutoassociativedynamicsgeneration2015, StellaHippocampalReactivationRandom2019}. We compute an estimate of how each cell's firing rate varies over position during movement (i.e. the place field, Figure \ref{1}B). This is used during decoding to compute the Poisson likelihood of position over time given the spiking sequence of interest. In contrast to the standard decoder, we can use small time bins (in our case 2 ms vs. 20 ms or more) because we are able to take advantage of the prior placed on the dynamics by the state space model. This allows us to detect changes on smaller time scales than would be possible with the standard decoder.

Next, we specify movement dynamic models for how latent position---the "mental" position of the animal represented by the cells---evolves over time for a given dynamic (Figure \ref{1}C). We do this by defining a state transition matrix, which defines how the latent position can move from the previous time step. Previous findings suggest that replay may exhibit at least three distinct types of movement dynamics: stationary \cite{JaiDistincthippocampalcorticalmemory2017, FarooqEmergencepreconfiguredplastic2019}, rapid continuous \cite{DavidsonHippocampalReplayExtended2009}, and fragmented, which could correspond to both extended spatially incoherent representations and representations that jump from one position to another in a short time period \cite{PfeifferAutoassociativedynamicsgeneration2015}. We therefore define state transition models to capture each of these movement dynamics.

In the stationary movement dynamic, the latent position does not change between time steps. The state transition matrix can thus be defined as an identity matrix, which predicts the next position will be the same as the last position. In the continuous movement dynamic, the latent position is most likely to be  "spatially close" to the position in the previous time step, so we use a Gaussian random walk state transition matrix. This means that, for a given latent position, the probability of moving to another position is modeled by a Gaussian centered at that position and "spatially close" is defined by the variance of the Gaussian. In our case, since replay has been shown to move at speeds much faster than the animal's speed \cite{DavidsonHippocampalReplayExtended2009, PfeifferAutoassociativedynamicsgeneration2015}, we set the variance of the Gaussian to 6.0 cm. This ensures that with a 2 ms time step, the latent position is 95\% likely to be within 4.90 cm of the previous latent position (or equivalently, this means that latent speeds from 0 to ~25 m/s are most likely).  Finally, in the fragmented movement dynamic, the latent position can move to any available position instantaneously. We model this using a uniform state transition matrix, which makes transitions to all positions equally likely.

Finally, we specify how likely each movement dynamic is to persist in time versus changing to another dynamic (Figure \ref{1}D) via a state transition matrix between dynamics. In order to be conservative, we assume that each movement dynamic is likely to dominate for \texttildelow100 ms, which is approximately the duration of a SWR event. There is, however, a small probability of switching to one of the other movement dynamics. Accordingly, we set the probability of staying in a dynamic to 0.98 for each 2 ms time step, which corresponds to an expected duration of 100 ms for staying in a particular dynamic. Importantly, the data drives the estimated dynamic, so even if the probability of a particular movement dynamic is high, data providing clear evidence for a change in dynamic can, within the time frame of \texttildelow10 ms, drive a change to a different estimated dynamic. In line with this, note that below we show that our results are relatively insensitive to the value of this parameter.

Once we have specified the data and the movement dynamics models, we have fully specified the state space model. We use acausal decoding, meaning that we use all information from the past and future spikes, to estimate the joint posterior probability of position and dynamic (see Methods). With this, we can summarize the resulting posterior with two quantities: the probability of each movement dynamic over time (by integrating out position) and the probability of latent position over time, irrespective of movement dynamic (by summing over the movement dynamics; Figure \ref{1}F, left and right plot respectively).

An examination of the two summaries shown in Figure \ref{1}F reveals that that the model successfully captures the dynamics of the population spiking activity in Figure \ref{1}A. The stable firing of the one active neuron indicates a stationary representation, and accordingly, the probability of the stationary movement dynamic is high at the beginning of the simulated replay. A change in the data then drives a rapid transition to the continuous movement dynamic, reflecting the trajectory-like spatially sequential spiking from the population of cells. Subsequently, as the population activity becomes spatially incoherent, the fragmented movement dynamic dominates for the last third of the simulated event.

The specification of these movement dynamics allows the model to capture a wide range of movement speeds for the latent position. To demonstrate this, we applied the model to 10,000 simulated trajectories, each trajectory proceeding at a constant speed (Figure \ref{1}G) from 1 cm/s to 10,000 m/s. From this, we can see that not only are there regions of speed that correspond to our three movement dynamics being highly probable (where we define highly probable to be greater than or equal to 0.8 probability), there are intermediate speeds where two of the dynamics exhibit relatively high probability; and where the sum of two of the dynamics' probabilities exceeds 0.8. In this manuscript, we will refer to these as mixture dynamics. For example, when the stationary state has a probability of 0.6 and the continuous has a probability of 0.4, we call this a stationary-continuous mixture (light blue, Figure \ref{1}G). By using this classification scheme, we can characterize the speed or set of speeds in a replay by its movement dynamics. To summarize, there are three movement dynamic models, each of which is assigned a probability over time. We classify these probabilities as being part of one of five speed categories: Stationary, Stationary-Continuous-Mixtures, Continuous, Fragmented-Continuous Mixtures, and Fragmented.

@@

One of our criteria for a more optimal method is for it to use all of the available spiking data. Using only clustered spikes discards any spike events that cannot be uniquely assigned to a putative single neuron, substantially reducing the amount of information that the resultant decoding can use. Additionally, spike sorting is not necessary to recover the underlying neural population dynamics \cite{TrautmannAccurateEstimationNeural2019}, is time-consuming, and often requires inclusion decisions that can vary widely across experimenters. We therefore adopted a "clusterless" approach which directly relates spikes and their multiunit spike waveform features to position without spike sorting, which we call clusterless decoding (see Methods). Clusterless decoding previously has been used to successfully identify theta sequences and replay sequences in the hippocampus \cite{KloostermanBayesiandecodingusing2014, ChenTransductiveneuraldecoding2012,DengRapidclassificationhippocampal2016, KayConstantSubsecondCycling2020}. Applying a clusterless decoder to the same SWR event, we get similar classification of the sequence (Figure \ref{2}B, D), both with 1D linearized position and 2D position (Figure \ref{fig:Figure2-Figure supplement 1}B). As predicted, the spatial extent of the event is longer and the estimate of the posterior probability of position is narrower for the clusterless model. This reflects the clusterless model's access to a larger pool of data that provides more information about the extent of the event and more certainty in the latent position and the dynamic (Figure \ref{2}D vs C).

@@

Using a 0.8 threshold, we were able to classify 89\% (23382 of 26160) of SWRs as containing at least one of the three dynamics or common state mixtures. To ensure that this depended on the sequential firing of spatially tuned cells in the hippocampus, we resampled position with replacement for two recording sessions, shuffling the relationship between spiking and spatial information and then fitting the encoding model. We then decoded the same SWR events containing the same spikes. Only 9\% of the SWRs were classified in the shuffled datasets, a value that was significantly less than that seen for the real data (p=0.02 for recording session 1, p=0.02 for recording session 2, Figure \ref{fig:Figure3-Figure supplement 2}).

@@

The authors declare that no competing interests exist.

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=1.0\linewidth]{figures/Figure1-supplemental1/Figure1_v3_supplemental1}
\caption{The model is robust to change of the probability of persisting in the same dynamic. Each plot shows the probability of each dynamic on simulated data example from Figure 1 with a different diagonal value---which governs the probability of remaining in that state. The off-diagonal values---the probability of switching to one of the other dynamics---are set to be equally likely with the remainder of the probability, as in Figure 1D. The first plot (upper left) shows the case when all dynamics are equally likely. The diagonal increases from left to right, top to bottom, until the case where the diagonal is one and the off-diagonal is zero---i.e. the case where there is no probability of switching to another state.}
\label{fig:Figure1-Figure supplement 1}
\end{figure*}
